Dependent Object Types

### 2012-06-29 doc/semester/report.tex
more templating

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}
\usepackage{listings}
\usepackage{alltt}

\lstdefinelanguage{Scala}%
{morekeywords={abstract,%
  case,catch,char,class,%
  def,else,extends,final,for,%
  if,import,implicit,%
  match,module,%
  new,null,%
  object,override,%
  package,private,protected,public,%
  for,public,return,super,%
  this,throw,trait,try,type,%
  val,var,%
  with,%
  yield,%
  lazy%
  },%
  sensitive,%
  morecomment=[l]//,%
  morecomment=[s]{/*}{*/},%
  morestring=[b]",%
  morestring=[b]',%
  showstringspaces=false%
}[keywords,comments,strings]%

\lstset{language=Scala,
  basicstyle=\scriptsize,
  columns=fullflexible
}

\newcommand{\code}[1]{\lstinline[language=Scala,columns=fixed,basicstyle=\ttfamily\small]|#1|}

@@

\begin{abstract}
% TODO
\end{abstract}

@@

I thank Adriaan Moors and Martin Odersky for fruitful discussions and
guidance.

>>>>

\input{dot_macros}

    \usepackage[pdftex,
                hyperindex,
                plainpages=false,
                breaklinks,
                colorlinks,
                citecolor=black,
                filecolor=black,
                linkcolor=black,
                pagecolor=black,
                urlcolor=black]{hyperref}
    \usepackage[pdftex]{graphicx}
    \DeclareGraphicsExtensions{.jpg,.pdf}
    \pdfcatalog {
        /PageMode (/UseNone)
    }
    \usepackage{thumbpdf}
    \usepackage[pdftex]{color}

@@

\begin{abstract}
In my semester project, I have studied a new proposed type-theoretic
foundation of Scala and languages like it: the Dependent Object Types
calculus (DOT). DOT models Scala's path-dependent types and abstract
type members, as well as its mixture of nominal and structural typing
through the use of refinement types. My ultimate goal was to prove DOT
sound, but instead, I found lots of counterexamples to soundness, and
have explored patches to the calculus.
\end{abstract}

\section{Introduction}

% TODO

\section{Counterexamples}

\section{Non-Expanding Types and Subtyping Transitivity}

@@

I thank Adriaan Moors and Martin Odersky for sharing previous work,
fruitful discussions and guidance.
